Radio Emission from Red-Giant Hot Jupiters

### 2015-12-02 ms.tex
minor edits

@@

As a whole, we expect for the X-ray emission from the accretion onto the planet to ionize the incoming stellar wind.
This implies that the stellar wind particles represented by equation (\ref{eq:n}) are nearly fully ionized plasmas like Solar wind, and that the stellar wind can interact with the planetary magnetic fields in a rather similar way to the case of Solar System planets.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
\label{s:result}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\revise{}{Let us also consider the expected number of radio detection from RGHJs taking account of the occurrence rate of Jovian planets. %
Observations suggest that the occurrence rate of planets with masses $M_{\rm J} < M_p \sin i < 2 M_{\rm J}$ in orbits $1 {\rm AU} < a < 5 {\rm AU}$ around F, G, or K stars is $\sim $ 3.9\% \citep{cumming2008}. %
%(Here we assume the rate does not change significantly in red giant stage, while admitting the likely orbital evolution at this stage. ) %
Given that 148 (12) systems with 1$M_{\rm J}$ planets at 1 AU (5 AU) have potential to emit $>10~\mu {\rm Jy}$, about 2-6 would actually be emitting the radio wave of our interest at the level of $>10~\mu {\rm Jy}$. %
For larger planets ($M_p>2M_{\rm J}$), the number of potentially detectable systems are less, due to both the $B^{-1/3}$ dependence of the spectral flux: the number of systems where a 10 $M_{\rm J}$ planet at 1 AU (5 AU) emit $>10~\mu {\rm Jy}$ is 98 (5): Since the occurrence rate of such larger planets in the same orbital region is $\sim 3.1\%$ \citep{cumming2008}, one could expect additional $\sim 1$ radio source detection from larger planets with sensitivity $10~\mu {\rm Jy}$. %
}

>>>>

As a whole, we expect for the X-ray emission from the accretion onto the planet to ionize the incoming stellar wind. 
\revise{This implies that the stellar wind particles represented by equation (\ref{eq:n}) are nearly fully ionized plasmas like Solar wind, and that the stellar wind can interact with the planetary magnetic fields in a rather similar way to the case of Solar System planets.}{}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Estimates}
\label{s:result}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@
